% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdflang={en},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
\babelprovide[import]{ngerman}
\babelprovide[import]{british}
\babelprovide[import]{nswissgerman}
\babelprovide[import]{spanish}
\babelprovide[import]{french}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\ifPDFTeX
  \TeXXeTstate=1
  \newcommand{\RL}[1]{\beginR #1\endR}
  \newcommand{\LR}[1]{\beginL #1\endL}
  \newenvironment{RTL}{\beginR}{\endR}
  \newenvironment{LTR}{\beginL}{\endL}
\fi

\author{}
\date{}

\begin{document}

\hypertarget{empty-divs-and-spans}{%
\section{Empty Divs and Spans}\label{empty-divs-and-spans}}

Some text and

div contents

and more text.

Next paragraph with a {span} and a word-thatincludesa{span}right?

\hypertarget{directionality}{%
\section{Directionality}\label{directionality}}

Some text and

\begin{RTL}
rtl div contents
\end{RTL}

and more text.

\begin{LTR}
and a ltr div. with a \RL{rtl span}.
\end{LTR}

Next paragraph with a \RL{rtl span} and a
word-that-includesa\LR{ltrspan}right?

\hypertarget{languages}{%
\section{Languages}\label{languages}}

Some text and

\begin{otherlanguage}{ngerman}

German div contents

\end{otherlanguage}

and more text.

Next paragraph with a \foreignlanguage{british}{British span} and a
word-that-includesa\foreignlanguage{nswissgerman}{Swiss German
span}right?

Some \foreignlanguage{spanish}{Spanish text}.

\hypertarget{combined}{%
\section{Combined}\label{combined}}

Some text and

\begin{RTL}
\begin{otherlanguage}{french}

French rtl div contents

\end{otherlanguage}
\end{RTL}

and more text.

Next paragraph with a \LR{\foreignlanguage{british}{British ltr span}}
and a word-that-includesa\LR{\foreignlanguage{nswissgerman}{Swiss German
ltr span}}right?

\end{document}
